### 2011-01-26 paper/problemDefinition.tex
Incorporated some of Jeff's suggestions

Mathematically, we define a gait as a function that specifies
a vector of commanded motor positions for a robot over time.
%Using this definition, we require one function per motor.
We can write gaits without feedback --- also called feedforward gaits
--- as

@@

%\noindent for commanded position $x_i$ for motor $i$.  The
\noindent for commanded position vector $\vec{x}$.  The
function depends only on time.  Using the same framework, a gait
including measured motor position, force, or other values could be
written as

\be
\vec{x} = g(t, \vec{z})
\ee

\noindent for some measurement vector $\vec{z}$.  Feedforward gaits
are deterministic (unless they include random elements), so they
produce the same command pattern each time they are run.  While the
commanded positions will be the same from trial to trial, the actual
robot motion and measured fitness will vary due to the noisiness of
trials in the real world.

The output of a gait that includes feedback, on the other hand,
depends on the actual measurements, and noise in these measurements
may result in different $\vec{x}$ values each time they are run.

>>>>

Mathematically, we define a gait as a function that specifies
a vector of commanded motor positions for a robot over time.
%Using this definition, we require one function per motor.
We can write gaits without feedback --- also called open-loop or
feedforward gaits --- as

@@

%\noindent for commanded position $x_i$ for motor $i$.  The
\noindent for commanded position vector $\vec{x}$.  The
function depends only on time.

%Using the same framework, a gait
%including measured motor position, force, or other values could be
%written as
%
%\be
%\vec{x} = g(t, \vec{z})
%\ee
%
%\noindent for some measurement vector $\vec{z}$.

It follows that feedforward gaits are deterministic, producing the
same command pattern each time they are run.  While the commanded
positions will be the same from trial to trial, the actual robot
motion and measured fitness will vary due to the noisiness of trials
in the real world.

%The output of a gait that includes feedback, on the other hand,
%depends on the actual measurements, and noise in these measurements
%may result in different $\vec{x}$ values each time they are run.
